Open, privacy-preserving protocols for lawful surveillance

### 2016-07-12 paper/submission.tex
Reformat to ACM double column

\documentclass[USenglish,oneside,twocolumn]{article}
\usepackage{etex}
\usepackage[utf8]{inputenc}%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
%\usepackage[big]{dgruyter_NEW}
\usepackage{amsmath}
\usepackage{hyperref}

@@

  \title{Open, privacy-preserving protocols for lawful surveillance}
  \author{
	Aaron Segal and Joan Feigenbaum \\
	Yale University \\
	New Haven, CT, USA
	\and
	Bryan Ford \\
	Swiss Federal Institute of Technology (EPFL) \\
	Lausanne, Switzerland}
  \date{}

@@

>>>>

%\documentclass[USenglish,oneside,twocolumn]{article}
\documentclass{sig-alternate-05-2015}

\usepackage{etex}
\usepackage[utf8]{inputenc}%(only for the pdftex engine)
%\RequirePackage[no-math]{fontspec}%(only for the luatex or the xetex engine)
%\usepackage[big]{dgruyter_NEW}
\usepackage{amsmath}
\usepackage{hyperref}

@@

  \title{Open, privacy-preserving protocols for lawful surveillance}
  \author{
	Aaron Segal and Joan Feigenbaum \\
	Yale University \\
	New Haven, CT, USA\\
	\{aaron.segal,joan.feigenbaum\}@yale.edu\\
	\and
	Bryan Ford \\
	Swiss Federal Institute of Technology (EPFL) \\
	Lausanne, Switzerland\\
	bryan.ford@epfl.ch}
  \date{}

@@

\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\doi{10.475/123_4}

% ISBN
%\isbn{123-4567-24-567/08/06}

%Conference
\conferenceinfo{WPES '16}{October 24, 2016, Vienna, Austria}

%\acmPrice{\$15.00}
